---
title: "art-code-CHOYOA-03"
author: "Graycen Mahon"
date: "2023-06-07"
output: html_document
---

## Task 1:
# Loading in Packages:

```{r}
library(ggplot2)
library(tibble)
```

# Exercise 1:

```{r}
mpg
```

```{r}
mpg |>
  # making the blank graph space
  ggplot(aes(displ, hwy, colour = drv))  + 
  # this line creates the box plot for the graph, and removes the legend from the plot. The size of the boxes are set to 2-
  geom_boxplot(show.legend = FALSE, size = 20)+ 
  # the next like adds anothe rboxplot, without a legend and making it outlines in orange (size 2.5).
  geom_boxplot(show.legend = FALSE, size = 2.5, colour = "orange") + 
  # coord polar makes the plot circular
  coord_polar() + 
  # theme void takes away the gridlines and plot details, other than the colors and shape I created. 
  theme_void()

```

# Exercise 2:

```{r}
# create an object called polar art and attach a function to it, so you can alter and change the specifics of the art piece created without having to type all this code over and over again. in the function, mention the characteristics you would like to be alterable. 
polar_art <- function(seed, n, palette) {
  
 # set the state of the random number generator which controls the size and number of values in the data frame used to make the art. 
  set.seed(seed)
  
  # data frame containing random values for aesthetics we might want to use in the art below. setting the x and y axis intervals using the runif function. the shade and size will correspond with the value of n chosen for each plot. 
  
    dat <- tibble(
    x0 = runif(n),
    y0 = runif(n),
    x1 = x0 + runif(n, min = -.2, max = .2),
    y1 = y0 + runif(n, min = -.2, max = .2),
    shade = runif(n), 
    size = runif(n)
  )
  
  # plot segments in various colors, using 
  # polar coordinates and a gradient palette
      dat |> 
    ggplot(aes(
      x = x0,
      y = y0,
      xend = x1,
      yend = y1,
      colour = shade,
      size = size
    )) +
    geom_segment(show.legend = FALSE)  +
    coord_polar() +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0))  + 
    scale_colour_gradientn(colours = palette) + 
    scale_size(range = c(0, 10)) + 
    theme_void()
      
# Lines 59-67 create a blank ggplot with the y and x axis set to equal intervals ending at 1.2
# line 68 makes a segment plot without a legend, with blue data points scattered in a large rectangular clump in the center of the plot.
# line 69: the coord polar function makes the plot circular
# lines 70-72 change the color palatte and side of the data segments
# line 74 takes away the grid lines of the plot as well as the axis values and titles. 
}
```

# My creations:

```{r}
# this one is inspired by cotton candy
polar_art(seed = 3, n = 200, palette = c("lightblue", "hotpink", "lightgreen"))
# this next one is inspired by the earth
polar_art(seed = 1, n = 500, palette = c("darkblue", "lightblue", "darkgreen"))
# this last one is inspired by my bedroom
polar_art(seed = 2, n = 600, palette = c("orange", "hotpink", "red", "lightblue"))
```

Creating my own function using the polar_art function

```{r}
polar_art_02 <- function(seed, n, palette) {
  
  # set the state of the random number generator which controls the size and number of values in the data frame used to make the art. 
  set.seed(seed)
  
  # data frame containing random values for aesthetics we might want to use in the art below. setting the x and y axis intervals using the runif function. the shade and size will correspond with the value of n chosen for each plot. 
  dat <- tibble(
    x0 = runif(n),
    y0 = runif(n),
    x1 = x0 + runif(n, min = -10, max = 10),
    y1 = y0 + runif(n, min = -3, max = 3),
    shade = runif(n), 
    size = runif(n)
  )
  
  # plot segments in various colors, using 
  # polar coordinates and a gradient palette
  dat |> 
    ggplot(aes(
      x = x0,
      y = y0,
      xend = x1,
      yend = y1,
      colour = shade,
      size = size
    )) +
    geom_segment(show.legend = FALSE) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0)) + 
    scale_colour_gradientn(colours = palette) + 
    scale_size(range = c(0, 10)) + 
    theme_void()
}

# Lines 116 - 124 create a blank ggplot with the y and x axis set to equal intervals ending at 1.2
# line 125 makes a segment plot without a legend, with blue data points scattered in a large rectangular clump in the center of the plot.
# lines 126-129 change the color palatte and side of the data segments
# line 130 takes away the grid lines of the plot as well as the axis values and titles. 

```

```{r}
# This first piece is inspired by a campfire
polar_art_02(seed = 1, n = 200, palette = c("red", "orange", "yellow"))
# the second is inspired by a stack of redwood tree logs
polar_art_02(seed = 2, n = 175, palette = c("tan", "brown", "black"))
# This last one is inspired by confetti
polar_art_02(seed = 3, n = 150, palette = c("red", "orange", "yellow", "green", "blue", "purple", "hotpink"))
```

# Loading in more packages for Exercise 3:

```{r}
library(scales)
library(ggthemes)
```

```{r}
pal <- c("#e78b28", "#ffe28a", "#fe9a83", "#ccabd8", "#9ac7a9")
# choose certain colors for your palatte (I got the hex codes off the internet)
show_col(pal)
# show the color palatte you are working with in a grid in the plot window
palette_fn <- colorRampPalette(pal)
# save a gradient palatte based on your color choices under palatee_fn
palette_fn(100)
# view 100 colors of your palatte!
```

```{r}
image(
  x = matrix(1:100, ncol = 1),
  col = palette_fn(100),
  useRaster = TRUE,
  axes = FALSE
)

# line 167 creates a matrix of colors on a graph of 100 colors in distinct columns
#line 168 blurs the color palatte together (like a gradient) and changes the colors within the graph to the palatte chosen in the code chunk above. 
# lines 169-170 remove the axis and labels from the graph to make it a rectangle of the gradient created. 
```

# Exercise 3:

```{r}
sample_canva <- function(seed = NULL) {
  if(!is.null(seed)) set.seed(seed)
  sample(ggthemes::canva_palettes, 1)[[1]]
}
# line 170 creates a new function called simple_canva and sets the seed to NULL which ensures that the code is not reproducible and will change every time the chunk is ran
# lines 180-181 calls on gg themes in order to pull colors from the canva palattes to create different color schemes each time the chunk is run. 

sample_canva(seed = NULL) %>% 
show_col()
# calling on the sample canva function and using the show_col function to make each palatte show in the plots window (bottom right)
```

```{r}
sample_named_colours <- function(seed, n = 4, palette) {
  set.seed(seed)
  sample(colours(distinct = FALSE))
}
# Lines 192-194: I made a new function called sample_named_colors and called upon the information seed, n, and palette. Then I set the seed value to to changed based on whatever each individual art piece deems it to be. Laslty I called on the colors function of r studio to set the palette sample. 
sampled_named_colours(seed = NULL, n = 100, palette = colours) %>% 
  show_col()
```

```{r trying-with-the-polar-art-funciton}
polar_art(seed = 56, n = 100, palette = sample_named_colours(seed = 1))
```

```{r all-600-colors-ggthemes}
unlist_sample_canva <- function(n, seed = NULL) {
  if(!is.null(seed)) set.seed(seed)
  unlist(ggthemes::canva_palettes)
}
```

```{r trying-with-the-polar-art-function}
polar_art(seed = 8, n = 100, palette = unlist_sample_canva(seed = 1))
```

# Exercise 4:

```{r sample-functions-from-repo}
sample_canva <- function(seed = NULL) {
  if(!is.null(seed)) set.seed(seed)
  sample(ggthemes::canva_palettes, 1)[[1]]
}

sample_data <- function(seed = NULL, n = 100){
  if(!is.null(seed)) set.seed(seed)
  dat <- tibble(
    x0 = runif(n),
    y0 = runif(n),
    x1 = x0 + runif(n, min = -.2, max = .2),
    y1 = y0 + runif(n, min = -.2, max = .2),
    shade = runif(n), 
    size = runif(n),
    shape = factor(sample(0:22, size = n, replace = TRUE))
  )
}

polar_styled_plot <- function(data = NULL, palette) {
  ggplot(
    data = data,
    mapping = aes(
      x = x0,
      y = y0,
      xend = x1,
      yend = y1,
      colour = shade,
      size = size
    )) + 
    coord_polar(clip = "off") +
    scale_y_continuous(
      expand = c(0, 0),
      limits = c(0, 1), 
      oob = scales::oob_keep
    ) +
    scale_x_continuous(
      expand = c(0, 0), 
      limits = c(0, 1), 
      oob = scales::oob_keep
    ) + 
    scale_colour_gradientn(colours = palette) + 
    scale_size(range = c(0, 10)) + 
    theme_void() + 
    guides(
      colour = guide_none(),
      size = guide_none(),
      fill = guide_none(),
      shape = guide_none()
    )
}
```

```{r example-artwork}
dat <- sample_data(n = 100, seed = 1) 
pal <- sample_canva(seed = 1)

polar_styled_plot(data = dat, palette = pal) + geom_segment()
polar_styled_plot(data = dat, palette = pal) + geom_path()
polar_styled_plot(data = dat, palette = pal) + geom_point()
```

```{r mutating-the-function-using-dplyr}
dat2 <- sample_data(n = 350, seed = 7)
dat3 <- sample_data(n = 666, seed = 12)
# creating new objects called dat2 and dat3 in order to adjust different data frames we can use to change the shape, color or configuration

polar_styled_plot(data = dat, palette = pal) + 
  # set the data and palette to the objects made in the code chunk above
  geom_point(data = dat2 |> mutate(size = size * 3)) + 
  # using geom_point, call on dat2 and mutate the size of the element
  geom_segment(data = dat3 |> mutate(size = size/200), 
  # then call on geom_segment and use data 3, also adjusting the size and color of the element
               colour = "hotpink")  + 
  geom_jitter(data = dat3 |> mutate(size = size/25), 
  # then call on geom_jitter again and use dat3, also adjusting the size and color of the element. I used a hex code to decide the color. 
               colour = "#764de4")
```

```{r creating-my-own-plot}
my_styled_plot <- function() {
  
}
```

```{r}
my_styled_plot(data = NULL, palatte)
```

## Task 2:
# Loading in packages 

```{r}
library(dplyr)
library(purrr)
library(tibble)
library(ggplot2)
library(ggthemes)
library(ambient)
```

# Excersise 1: 

```{r first-ambient-plot-mutate}
sample_canva <- function(seed = NULL) {
  if(!is.null(seed)) set.seed(seed)
  sample(ggthemes::canva_palettes, 1)[[1]]
}
# lines 329 - 331 set the "window" of view for the image, I altered the original code to zoom out. 
x_coords <- seq(from = -1, to = 2, length.out = 550)
y_coords <- seq(from = -1, to = 2, length.out = 550)
canvas <- long_grid(x = x_coords, y = y_coords) 
# lines 334-336 alter the spacing, color and frequency of the art piece. I changed the first and third vlaues in order to change the size and color of the piece. 
freq_spatial <- 25
seed_spatial <- 100
seed_palette <- 32

# I just changed the generator function below in order to change the overall structure of the art. I kept the rest of the code the same. 
dat <- canvas |> 
  mutate(
    paint = gen_waves(
      x = x, 
      y = y, 
      frequency = freq_spatial, 
      seed = seed_spatial
    )
  )
# lines 349 - 358 adjust the shape and layout of the grid. It removes the legend, grid lines, axis labels and plot shading. 
pic <- dat |>
  ggplot(aes(x, y, fill = paint)) + 
  geom_raster(show.legend = FALSE) +
  theme_void() + 
  coord_equal() +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_gradientn(
    colours = sample_canva(seed_palette)
  )
# viewing the artwork
plot(pic)
```

# Exercise 2:

```{r make-noise-art-mutation}
make_noise_art <- function(
    generator = gen_worley, 
# I changed the original code generator from perlin to worley in order to get a different shaped output.
    frequency = 5, seed = 1500, 
# i changed the frequency and seed in the lines above to alter the spacing, pixel concentration and positioning of the artwork. 
    pixels = 5000, 
# I also changed the original code to show more pixels, and therefore a wider view of the artwork and then in lines 375, I changed the color palatte used in the piece. I used a palatte generated by R studio and copied the hex codes. 
    palette = c("#bfd8d2", "#fedcd2", "#df744a", "#dcb239")) {
  
  # define the grid
  # lines 379-381 are used to set the size of the grid, I decided to expand it from 0 -> 1 to -1 -> 2 to make the image slightly larger. I also kept the fact that the x and y axis would have the same grid length, so the image would be a square. 
  canvas <- long_grid(
    x = seq(from = -1, to = 2, length.out = pixels),
    y = seq(from = -1, to = 2, length.out = pixels)
  ) 
  
  # use the generator to add paint
  canvas <- canvas |>
    mutate(
      paint = generator(
        x, y, 
        frequency = frequency, 
        seed = seed)
    )
# Lines 381-386 fill the screen with paint palatte from line 372 and set the seed and frequency equal to values in lines 370. Without the canvas object and using the generator to add paint, the artwork is just a dark screen with no dimension. 
  
  # use ggplot2 to draw the picture
  art <- canvas |> 
    ggplot(aes(x, y, fill = paint)) + 
    geom_raster(show.legend = FALSE) +
    theme_void() +
    coord_equal() +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_fill_gradientn(colours = palette)
  
# lines 395-402 removed plot lines, the legend and the axis values and then uses the x and y scale function to set the color palatte to gradient so the colors come out "ombre". Line 402 sets the color palate to the one chosen in line 375 and makes the whole plot gradient. 
  return(art)
}

```

```{r artwork}
make_noise_art(seed = 666)
make_noise_art(seed = 1212)
make_noise_art(seed = 5463)
```

2.2:
I literally have no clue how to ensure each image is saved individually. 

# Exercise 3:

```{r creating-a-blank-canvas}
sample_canva <- function(seed = NULL) {
  if(!is.null(seed)) set.seed(seed)
  sample(ggthemes::canva_palettes, 1)[[1]]
}

blank_canvas <- long_grid(
  x = seq(from = 0, to = 1, length.out = 2000),
  y = seq(from = 0, to = 1, length.out = 2000)
) 

plot_painted_canvas <- function(canvas, palette = NULL) {
  if(is.null(palette)) {
    palette <- c("#e5ddc8","#01949a","#004369","#db1f48")
  }
  canvas |> 
    ggplot(aes(x, y, fill = paint)) + 
    geom_raster(show.legend = FALSE) +
    theme_void() +
    coord_equal() +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_fill_gradientn(colours = palette)
}

# your code here! add to the blank canvas
blank_canvas |> 
  mutate(
    lf_noise = gen_waves(x, y, frequency = 6),
    mf_noise = gen_spheres(x, y, frequency = 12),
    hf_noise = gen_perlin(x, y, frequency = 85),
    gate = gen_simplex(x, y, frequency = 10) |> normalise(),
    paint = lf_noise + mf_noise + hf_noise
  ) |>
  plot_painted_canvas(palette = sample_canva(seed = 12))

```

# Exercise 4:

```{r}
sample_canva <- function(seed = NULL) {
  if(!is.null(seed)) set.seed(seed)
  sample(ggthemes::canva_palettes, 1)[[1]]
}

blank_canvas <- long_grid(
  x = seq(from = 0, to = 1, length.out = 2000),
  y = seq(from = 0, to = 1, length.out = 2000)
) 

plot_painted_canvas <- function(canvas, palette = NULL) {
  if(is.null(palette)) {
    palette <- c("#e5ddc8","#01949a","#004369","#db1f48")
  }
  canvas |> 
    ggplot(aes(x, y, fill = paint)) + 
    geom_raster(show.legend = FALSE) +
    theme_void() +
    coord_equal() +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_fill_gradientn(colours = palette)
}

fractal_art <- function(fractal, generator, palette = NULL, ...) {
  blank_canvas |>
    mutate(
      paint = fracture(
        noise = generator,
        fractal = fractal,
        x = x, 
        y = y, 
        ...
      )
    ) |>
    plot_painted_canvas(palette = palette)
}
```


```{r}
gf <- function(x) x * 0.1
new_gain <- function(x) x * 0.2
new_frequency <- function(x) x * 0.5
fractal_art(fractal = ridged, 
            generator = gen_simplex, 
            seed = 12, 
            octaves = 3, 
            gain = gf, 
            frequency = new_frequency)

# ambient artwork
x_coords <- seq(from = 0, to = 2, length.out = 950)
y_coords <- seq(from = 0, to = 2, length.out = 950)
```


```{r}
canvas <- long_grid(x = x_coords, y = y_coords) 

gen_worley(x = 1:5, y = 1, frequency = .001, seed = 1)
gen_worley(x = 1:5, y = 1, frequency = .5, seed = 1)

canvas <- canvas |> 
  mutate(paint = gen_worley(x, y, frequency = 10, seed = 1234))
canvas

art <- ggplot(canvas, aes(x, y, fill = paint)) + 
  geom_raster(show.legend = FALSE) 

art + 
  theme_void() +
  coord_equal() +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_gradientn(colours = palette())

make_noise_art <- function(
    generator = gen_worley, 
    frequency = 43, 
    seed = 5463,
    pixels = 3000,
    palette = palette
) {
  
  # define the grid
  canvas <- long_grid(
    x = seq(from = -1, to = 1, length.out = 395),
    y = seq(from = -1, to = 1, length.out = 395)
  ) 
  
  # use the generator to add paint
  canvas <- canvas |>
    mutate(
      paint = generator(
        x, y, 
        frequency = frequency, 
        seed = seed, 
        palette = palette
      )
    )
  
  # use ggplot2 to draw the picture
  art <- canvas |> 
    ggplot(aes(x, y, fill = palette)) + 
    geom_raster(show.legend = FALSE) +
    theme_void() +
    coord_equal() +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_fill_gradientn(colours = palette)
  
  
  
  show_col(make_noise_art)
}
```

```{r}
fbm <- function(base, new, strength, ...) {
  base + new * strength
}

blank_canvas |>
  mutate(
    lf_noise = gen_waves(x, y, frequency = 33),
    mf_noise = gen_worley(x, y, frequency = 20),
    hf_noise = gen_waves(x, y, frequency = 99),
    gate = gen_simplex(x, y, frequency = 10) |> normalise(),
    paint = lf_noise +
      (1 + mf_noise) * (gate >= .1 & gate < .6) +
      (1 + hf_noise) * (gate >= .05)
  )

fractal_art(fbm, gen_checkerboard, seed = 1, octaves = 1)
fractal_art(fbm, gen_checkerboard, seed = 1, octaves = 2)
fractal_art(fbm, gen_checkerboard, seed = 1, octaves = 20)

blank_canvas |>
  mutate(paint = gen_worley(x, y, seed = 6)) |>
  plot_painted_canvas()
```

Note: 
I have been working on this Task for days. I have no idea what the frick is going on so I'm just going to move on because I honestly can't keep doing this. I tried to go through one line at a time but my computer is taking 10 minutes to load each time I run the code chunk and I do not have that kind of time with all my other finals and needing to start this final. 

## Exercise 5:

```{r}
curl_data <- function(
    data, 
    iterations = 50,
    step_size = .001,
    ...
) {
  
  update <- function(current_state, iteration, ...) {
    curl <- curl_noise(
      x = current_state$x, 
      y = current_state$y,
      generator = fracture,
      ...
    )
    next_state <- current_state |>
      mutate(
        x = x + curl$x * step_size,
        y = y + curl$y * step_size,
        time = time + 1
      )
    return(next_state)
  }
  
  data |> 
    mutate(id = row_number(), time = 1) |>
    accumulate(1:iterations, update, .init = _, ...) |>
    bind_rows()
}

curl_art <- function(...) {
  curl_data(...) |> 
    ggplot(aes(x, y, group = id)) + 
    geom_path() +
    theme_void() + 
    coord_equal() 
}

smol_grid <- long_grid(x = 1:20, y = 1:20)

pic <- smol_grid |>
  mutate(x = normalise(x), y = normalise(y)) |>
  curl_art(noise = gen_simplex, fractal = fbm, octaves = 4, freq_init = .5)

tic()
ggsave(
  filename = here("output", "curl-art-1.png"), 
  plot = pic,
  width = 2000,
  height = 2000,
  units = "px",
  dpi = 300,
  bg = "white"
)
toc()
```

```{r}
curl_data <- function(
    data, 
    iterations = 50,
    step_size = .001,
    ...
) {
  
  update <- function(current_state, iteration, ...) {
    curl <- curl_noise(
      x = current_state$x, 
      y = current_state$y,
      generator = fracture,
      ...
    )
    next_state <- current_state |>
      mutate(
        x = x + curl$x * step_size,
        y = y + curl$y * step_size,
        time = time + 1
      )
    return(next_state)
  }
  
  data |> 
    mutate(id = row_number(), time = 1) |>
    accumulate(1:iterations, update, .init = _, ...) |>
    bind_rows()
}

curl_art <- function(...) {
  curl_data(...) |> 
    ggplot(aes(x, y, group = id)) + 
    geom_path() +
    theme_void() + 
    coord_equal() 
}

custom_curl_data <- function(data) {
  curl_data(
    data = data,
    iterations = 80, 
    octaves = 10,
    fractal = ridged,
    noise = gen_cubic,
    freq_init = 1,
    frequency = ~ . * 1.2,
    gain_init = 1,
    gain = ~ . * .9,
    seed = 1
  )
}

circle <- function(n = 100) {
  tibble(
    theta = 2 * pi * (1:n) / n, 
    x = cos(theta),
    y = sin(theta)
  )
}

dat1 <- circle(5000) |> 
  custom_curl_data()

dat2 <- circle(5000) |>
  mutate(x = x * .99, y = y * .99) |>
  custom_curl_data()

pic <- ggplot(mapping = aes(x, y, group = time)) +
  geom_polygon(data = dat1, fill = "#ffffff10") +
  geom_polygon(data = dat2, fill = "#22222205") +
  theme_void() +
  coord_equal()

tic()
ggsave(
  filename = here("output", "curl-art-2.png"), 
  plot = pic,
  width = 2000,
  height = 2000,
  units = "px",
  dpi = 300,
  bg = "white"
)
toc()
```

I literally don't know what's going on I am so confused

## Task 3:

Honestly I can't stop crying and I really can't do this I'm just going to take a poor grade and move on. This is supposed to be a "fun" assignment, but it's given me more anxiety and frustration than any other class & assignment I have ever done in my life. 
